PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-09-10 qfenv_paper/qf_environment.tex
Major changes to Section 4 organization
Made Comparison to Literature section.
Addressed comments by Mike Blanton.
Comparison to literature section not finished!

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$. The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\citealt{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\citealt{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: dex$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right panel) and low (left panel) density environments. As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width. For the uncertainty in the quiescent fraction, we use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}.

@@

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\citealt{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments, a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\citealt{Noeske:2007aa, cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\citealt{hopkins06a}). %Maybe Stacey et al. 2014 is relevant here?

@@

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements with analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with previous SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).

At higher masses, our $f_{\rm{Q}}$ results are consistent with \cite{Baldry:2006aa}. \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although in these comparisons, the different environment measurements make direct comparisons unclear, at higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, in agreement our high density environment. Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.

@@

Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we naively account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are generally consistent with our $f_{\rm{Q}}$ at high and low density environments. However, in their higher redshift bin even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.

We previously addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases. This general trend is in good agreement with \cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{blue}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$. However, in contrast to our $f_{\rm{Q}}$ redshift evolution, \cite{Kovac:2014aa} presents a notable decrease in $f_{\rm{red}}$ over cosmic time for low environment. Even for their galaxies in high density environments, \cite{Kovac:2014aa} finds no significant increase in $f_{\rm{red}}$ with cosmic time.

>>>>

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=0}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments from redshift range $z=0-0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=2 \: \rm{Mpc}$ and $H=25 \: \rm{Mpc}$ and  
classification based on the cut-offs specified in Table \ref{tab:aperture}. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.25$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or star-forming and low or high density environments. We further divide these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$, $0.4-0.6$, and $0.6-0.8$ for a total 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies ($N$) per unit volume within the stellar mass range $[\rm{log} \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log} \:\mathcal{M})]$. The equation above is same as Equation 3. in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

While the fractional relation of the star-forming and quiescent populations has been investigated in the past, with limited statistics, disentangling the environmental effects f rom underlying correlations among observable galaxy properties such as the color-mass or mass-density relations (\citealt{Cooper:2010aa}) remains a challenge. With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass, redshift, and environment in Section \ref{sec:qfevol}. By analyzing the quiescent fraction with respect to these properties, in Section \ref{sec:env_qf_evol} we explicitly compare the quiescent fraction evolution in low and high density environments. Our comparison reveal the subtle environmental effects on the quiescent fraction evolution. Furthermore, by quantifying this environmental effect, we are able constrain the role of environmental quenching in galaxy evolution.
%With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\citealt{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\citealt{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: \mathrm{dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right panel) and low (left panel) density environments. As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width. For the uncertainty in the quiescent fraction, we use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}.

@@

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases. For high density environments, this is analogous to the Butcher-Oemler Effect (\citealt{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments, a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\citealt{Noeske:2007aa, cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\citealt{hopkins06a}). %Maybe Stacey et al. 2014 is relevant here?

@@

Finally, we compare between our low and high density environment $f_{\rm{Q}}$s at each redshift bin interval. For our lowest redshift bin, we find that $f_{\rm{Q}}$ at low density environments ranges from $\sim 0.4$ to $\sim 0.8$ for $10^{10.2} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$. Over the same mass range, $f_{\rm{Q}}$ at high density environment ranges from $\sim 0.55$ to $\sim 0.9$. Evidently for our SDSS sample, $f_{\rm{Q}}$ in high density environment is notably higher.

For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.15$ to $\sim 0.55$ for low density environment, while at high density environment $f_{\rm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.7$. Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\rm{Q}}$ ranges from $\sim 0.25$ to $\sim 0.55$ for low density environment and $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$. Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\rm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.55$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density. For the entire redshift range of our sample, $f_{\rm{Q}}$ in high density environment is higher than $f_{\rm{Q}}$ in low density environments.

While there is a significant difference in $f_{\rm{Q}}$ between the environments, since the difference is observed from our highest redshift bin it is not necessarily a result of environment dependent quenching mechanisms. In order to isolate the environmental dependence on star-formation quenching, in the following section we quantitatively compare the evolution of the quiescent fraction between the different environments.

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}})$, for low (blue) and high (red) density environments within the redshift range $z = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\rm{fid}})$ evolution for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot$ (solid fill) and $10^{11} \mathcal{M}_\odot$ (patterned fill) with the uncertainty of the best-fit parameter $b$ in Equation \ref{eq:qffit} represented by the width of the evolution. While the high density $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ is greater than low density environment $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over the entire redshift range of our sample, there is a significant increase in $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ over cosmic time for both environments. For the environment cut-offs ($n_{\rm{env}} < 0.5$ for low and $n_{\rm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} \label{eq:qffit}
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\rm{fid}}} \right)+b,
\end{equation}
where $a$ and $b$ are best-fit parameters using {\em MPFIT} (\citealt{Markwardt:2009aa}) and $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies. We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$.

In Figure \ref{fig:qffit} we present the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ at low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill). The width of the evolution represents the uncertainty derived from {\em MPFIT}. As noted earlier in Section \ref{sec:qfevol}, $f_{\rm{Q}}$ in high density environment is significantly greater than $f_{\rm{Q}}$ in low density environment for both fiducial mass choices. Throughout our sample's redshift range $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{high}} - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})_{\mathrm{low}} \sim 0.1$

In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution illustrates that the quiescent fraction at low redshift increases over cosmic time: $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$. This significant quiescent fraction evolution suggests that internal mechanisms independent of environment are responsible for a significant amount of star-formation quenching. The $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.

When we increase our choice of $\mathcal{M}_{\rm{fid}}$ to $10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.1$ from $z \sim 0.7$ to $\sim 0.1$. Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the evolutionary trends in either environments. Although the varying stellar mass completeness at each redshift bin limits the masses we probe for the $f_{\rm{Q}}$ evolution, our $f_{\rm{Q}}$ evolution exhibits little mass dependence.

Considering that our fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, in Figure \ref{fig:qffit_comp}, we impose more stringent high density environment classifications, extending the cut off to $n_{\mathrm{env}} > 6$ and $9$ (specified in the top right legend and represented by the color of the shading). Aside from the increase in uncertainties that accompany a decrease in sample size from a purer high environment sample, we find an extension of the $f_{\rm{Q}}$ difference between the environments we stated earlier. A more stringent high environment classification significantly increases the overall $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$: $f_{\mathrm{Q}, n_{\mathrm{env}}>9} > f_{\mathrm{Q}, n_{\mathrm{env}}>6} > f_{\mathrm{Q}, n_{\mathrm{env}}>3} > f_{\mathrm{Q}, n_{\mathrm{env}}<0.5} $.

More importantly, a purer high environment classification reveals a more significant environment dependence on the $f_{\rm{Q}}$ evolution. While the difference between the $f_{\rm{Q}}$ evolution in low and high density environment is negligible for the $n_{\rm{env}} > 3$ cut-off, there is a notable difference in $f_{\mathrm{Q}}$ evolution between our highest cut-off $n_{\rm{env}} > 9$ and our low density environment. $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.2$ for $n_{\rm{env}} > 9$ versus $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$ for low density environment as we listed earlier. In addition to the environment independent internal quenching mechanisms that can explain the $f_{\rm{Q}}$ evolution at low density environments, there may be other environment dependent mechanisms that can account for the moderate environment dependence of the $f_{\rm{Q}}$ evolution. Our measured difference in the $f_{\rm{Q}}$ evolution between environments provides a strict constraint for any environmental quenching models.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COMPARISON TO LITERATURE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison to Literature}
Although a direct comparison with other results is impossible due to our sample specific methodology, a number of results from literature have investigated the quiescent fraction. In this section we compare our $f_{\rm{Q}}$ results from above to a number of these results, specifically from SDSS and zCOSMOS, with comparably defined samples and analogous environment classifications.

For our lowest redshift bin SDSS sample, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with other SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment. For example, \cite{Baldry:2006aa} uses project neighbor density environment measures ($\rm{log} \;  \Sigma$) to obtain $f_{\rm{Q}}(\mathcal{M})$ for a range of environmental densities. Although the different environment measurements make direct comparisons unclear, in their corresponding higher environments ($\rm{log} \; \Sigma > 0.2$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.6$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.9$, which is in agreement with our high density environment. Likewise, for lower environments ($\rm{log} \; \Sigma < -0.4$ in \citealt{Baldry:2006aa}) $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.4$ and $f_{\rm{Q}}(\mathcal{M} \sim 10^{11.5} \mathcal{M}_{\odot}) \sim 0.8$, which also agree with our low density environment $f_{\rm{Q}}$.

More recently, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).

A modified \cite{Tinker:2011aa} sample is used in \cite{geha12a} to obtain $f_{\rm{Q}}$ for isolated galaxies over a wider mass range ($10^{7.4} \mathcal{M}_\odot$ to $10^{11.2} \mathcal{M}_{\odot}$). Provided that \cite{geha12a} probe a slightly lower redshift range ($ z \le 0.06$), \cite{geha12a} present a consistent $f_{\rm{Q}}$ range as our SDSS $f_{\rm{Q}}$. Within the overlapping mass range, at the low mass end \cite{geha12a} find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{10.2} \mathcal{M}_{\odot}) \sim 0.3$ and at the high mass end they find $f_{\rm{Q}}(\mathcal{M}_{*} \sim 10^{11.2} \mathcal{M}_{\odot}) \sim 0.8$. Both of these values agree with our lowest redshift $f_{\rm{Q}}$ results.

@@

Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. While for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$. Although \cite{Kovac:2014aa} does not elaborate on how the galaxy classification discrepancy applies to the different environments, if we simply account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin are roughly consistent with our $f_{\rm{Q}}$ at high and low density environments. However, in their higher redshift bin even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.

As we did for our $f_{\rm{Q}}$ analysis above, we extend our $f_{\rm{Q}}$ comparison to focus on the evolution of the quiescent fraction at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$. In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond). From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the difference between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$). We also plot $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot})$ from \cite{geha12a}.
